---
title: "Module-8-Zombie"
output: html_document
---

#Zombie
```{r}
library(curl)
f <- f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall17/zombies.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
```
#Zombie[1]
```{r}
h <- d$height
meanh <- mean(h)
meanh
```
above is the mean height of the population
```{r}
pop_v <- function(h) {
    sum((h - mean(h))^2)/(length(h))
}
pop_sd <- function(h) {
    sqrt(pop_v(h))
}
pop_sd(h)
```
above is the poulation SD for height
```{r}
w <- d$weight
meanw <- mean(w)
meanw
```
above is the mean weight
```{r}
pop_v <- function(w) {
    sum((w - mean(w))^2)/(length(w))
}
pop_sd <- function(w) {
    sqrt(pop_v(w))
}
pop_sd(w)
```
above is the population SD for weight

```{r}
a <- d$age
meana <- mean(a)
meana
```
above is the mean age

```{r}
pop_v <- function(a) {
    sum((a - mean(a))^2)/(length(a))
}
pop_sd <- function(a) {
    sqrt(pop_v(a))
}
pop_sd(a)
```
above is the population SD for age

```{r}
z <- d$zombies_killed
meanz <- mean(z)
meanz
```
above is the mean number of zombies killed

```{r}
pop_v <- function(z) {
    sum((z - mean(z))^2)/(length(z))
}
pop_sd <- function(z) {
    sqrt(pop_v(z))
}
pop_sd(z)
```
above is the population SD for number of zombies killed

```{r}
y <- d$years_of_education
meany <- mean(y)
meany
```
above is the mean of the years of education

```{r}
pop_v <- function(y) {
    sum((y - mean(y))^2)/(length(y))
}
pop_sd <- function(y) {
    sqrt(pop_v(y))
}
pop_sd(y)
```
above is the population SD for years of education

#Zombie[2]

```{r, eval=FALSE}
ph <- ggplot(data = d, aes(x = gender, y =height))
ph <- ph + geom_boxplot()
ph <- ph + theme(axis.text.x = element_text(angle = 90))
ph <- ph + ylab("height")
ph
```
above is the boxplot for height
```{r, eval=FALSE}
pw <- ggplot(data = d, aes(x = gender, y =weight))
pw <- pw + geom_boxplot()
pw <- pw + theme(axis.text.x = element_text(angle = 90))
pw <- pw + ylab("weight")
pw
```
above is the boxplot for weight
```{r, eval=FALSE}
pa <- ggplot(data = d, aes(x = gender, y =age))
pa <- pa + geom_boxplot()
pa <- pa + theme(axis.text.x = element_text(angle = 90))
pa <- pa + ylab("age")
pa
```
above is the boxplot for age
```{r, eval=FALSE}
pz <- ggplot(data = d, aes(x = gender, y =zombies_killed))
pz <- pz + geom_boxplot()
pz <- pz + theme(axis.text.x = element_text(angle = 90))
pz <- pz + ylab("number of zombies killed")
pz
```
above is the boxplot for the the number of zombies killed
```{r, eval=FALSE}
py <- ggplot(data = d, aes(x = gender, y =years_of_education))
py <- py + geom_boxplot()
py <- py + theme(axis.text.x = element_text(angle = 90))
py <- py + ylab("years of education")
py
```
above is the boxplot for years of education

#Zombies[3]
```{r, eval=FALSE}
psh <- ggplot(data = d, aes(x = age, y = height))  
psh <- psh + xlab("age") + ylab("height")  
psh <- psh + geom_point()  
psh <- psh + theme(legend.position = "bottom", legend.title = element_blank())  
psh

psw <- ggplot(data = d, aes(x = age, y = weight))  
psw <- psw + xlab("age") + ylab("weight")  
psw <- psw + geom_point()  
psw <- psw + theme(legend.position = "bottom", legend.title = element_blank())  
psw
```
The variable of hight andand weight to age both seem to be related. As age increases so does height. It looks like a positive linear coralation.  

#Zombie[4]
```{r}
minh <- min(d$height)
minh

maxh <- max(d$height)
maxh
```
here I took the min and hax for height so I could make my histograms
```{r}
qqnorm(d$height, main="normal QQ plot for height")
qqline(d$height, col="blue")
hist(d$height, breaks = seq(from =50, to =100, by=5), probability= TRUE)
```
The distrabutioin above for height looks normal
```{r}
minw <- min(d$weight)
minw

maxw <- max(d$weight)
maxw
```
```{r}
qqnorm(d$weight, main="normal QQ plot for weight")
qqline(d$weight, col="blue")
hist(d$weight, breaks = seq(from =80, to =250, by=5), probability= TRUE)
```
The distrabutioin above for weight looks normal

```{r}
mina <- min(d$age)
mina

maxa <- max(d$age)
maxa
```
```{r}
qqnorm(d$age, main="normal QQ plot for age")
qqline(d$age, col="blue")
hist(d$age, breaks = seq(from =5, to =35, by=1), probability= TRUE)
```
The distrabutioin above for age looks normal

```{r}
minz <- min(d$zombies_killed)
minz

maxz <- max(d$zombies_killed)
maxz
```
```{r}
qqnorm(d$zombies_killed, main="normal QQ plot for Zombies killed")
qqline(d$zombies_killed, col="blue")
hist(d$zombies_killed, breaks = seq(from =0, to =11, by=1), probability= TRUE)
```
The distrabutioin above for number of zombies looks poisson

```{r}
minz <- min(d$years_of_education)
minz

maxz <- max(d$years_of_education)
maxz
```
```{r}
qqnorm(d$years_of_education, main="normal QQ plot for years of education")
qqline(d$years_of_education, col="blue")
hist(d$years_of_education, breaks = seq(from =0, to =11, by=1), probability= TRUE)
```
The distrabutioin above for number of zombies looks poisson
#Zombies[5]
```{r}
samp <- d[sample(nrow(d), 30, replace = FALSE, prob = NULL),  ]
samp
```
above is the sample data from d
```{r}
samph <- samp$height
meansh <- mean(samph)
meansh

sampvarh <- var(samph)
sampSDh <- sqrt(sampvarh)
sampSDh

sampSEh <- sqrt(sampvarh/30)
sampSEh

upperh <- qnorm( 0.95, mean=meansh, sd=sampSDh)
upperh

lowerh <- qnorm( 0.05, mean=meansh, sd=sampSDh)
lowerh

cih <- c(lowerh, upperh)
cih
```
above are the sample SD and sample mean, sample SE, and the CI is 61.42163 to 74.47413 of height, 
```{r}
sampw <- samp$weight
meansw <- mean(sampw)
meansw

sampvarw <- var(sampw)
sampSDw <- sqrt(sampvarw)
sampSDw

sampSEw <- sqrt(sampvarw/30)
sampSEw

upperw <- qnorm( 0.95, mean=meansw, sd=sampSDw)
upperw

lowerw <- qnorm( 0.05, mean=meansw, sd=sampSDw)
lowerw

ciw <- c(lowerw, upperw)
ciw
```

above are the sample SD, sample mean, sample SE and the CI is from 100.1978 to 176.3308 of weight
```{r}
sampa <- samp$age
meansa <- mean(sampa)
meansa

sampvara <- var(sampa)
sampSDa <- sqrt(sampvara)
sampSDa

sampSEa <- sqrt(sampvara/30)
sampSEa

uppera <- qnorm( 0.95, mean=meansa, sd=sampSDa)
uppera

lowera <- qnorm( 0.05, mean=meansa, sd=sampSDa)
lowera

cia <- c(lowera, uppera)
cia
```
above are the sample SD sample mean, SE and the CI is from 14.13943 to 25.17132f of age
```{r}
sampz <- samp$zombies_killed
meansz <- mean(sampz)
meansz

sampvarz <- var(sampz)
sampSDz <- sqrt(sampvarz)
sampSDz

lambdaz <- (sum(sampz)/30)
lengthz <- length(sampz)
sez <- sqrt(lambdaz/lengthz)
sez
upperz <- lambdaz+ 1.96*sez
lowerz <- lambdaz- 1.96*sez
ciz <- c(lowerz, upperz)
ciz

```
above are the sample SD mean, se and the ci is from 2.49903 to 3.766764 of zombies killed
```{r}
sampy <- samp$years_of_education 
meansy <- mean(sampy)
meansy

sampvary <- var(sampy)
sampSDy <- sqrt(sampvary)
sampSDy

lambday <- (sum(sampy)/30)
lengthy <- length(sampy)
sey <- sqrt(lambday/lengthy)
sey
uppery <- lambday+ 1.96*sey
lowery <- lambday- 1.96*sey
ciy <- c(lowery, uppery)
ciy
```
above are the sample mean, sd, se and the ci is from 2.320452 to 3.546214 of years of education

#Zombie[6]
```{r}
new30height <- NULL
for (i in 1:100) {
    new30height[i] <- mean(sample(d$height,30))
}

hist(new30height,probability = TRUE)
```
this is the random new sample of 30 individuals 100 times for height
```{r}
mean(new30height)
sd(new30height)
```
these are the mean and sd for the new samples of height
```{r}
new30weight <- NULL
for (i in 1:100) {
    new30weight[i] <- mean(sample(d$weight,30))
}

hist(new30weight,probability = TRUE)
```
this is the random new sample of 30 individuals 100 times for weight
```{r}
mean(new30weight)
sd(new30weight)
```
these are the mean and sd for the new samples of weight
```{r}
new30age<-NULL
for (i in 1:100) {
    new30age[i] <- mean(sample(d$age,30))
}

hist(new30age,probability = TRUE)
```
this is the random new sample of 30 individuals 100 times for age
```{r}
mean(new30age)
sd(new30age)
```
these are the mean and sd for the new samples of age
```{r}
new30zombieskilled<-NULL
for (i in 1:100) {
    new30zombieskilled[i] <- mean(sample(d$zombies_killed,30))
}

hist(new30zombieskilled,probability = TRUE)
```
this is the random new sample of 30 individuals 100 times for number of zombeis killed
```{r}
mean(new30zombieskilled)
sd(new30zombieskilled)
```
these are the mean and sd for the new samples of number of zombies killed
```{r}
new30education<-NULL
for (i in 1:100) {
    new30education[i] <- mean(sample(d$years_of_education,30))
}

hist(new30education,probability = TRUE)
```
this is the random new sample of 30 individuals 100 times for years of education 
```{r}
mean(new30education)
sd(new30education)
```
these are the mean and sd for the new samples of years of education
these new sd are very similar to the se, they are not exact, but they are similar. all of these samples for the most part look normal more or less. Even the variables that looks like a poisson distrabutiom (the number of zombies killed and years of education) are now normal looking after taking the mean and sd of a sample 100 times 








